Multi-level modeling with Openflexo/\FML

### 2022-03-25 4-technology.tex
fix space between footnote number and punctuation

A parallel to object-oriented approach can be useful to understand
\FML\footnote{Some features of \FML do not exist in object oriented approach.}.
A concept corresponds to a class, its properties to the attributes of the class
and its behaviors to the methods of the class. These properties have types
defining the kind of value the role will point at runtime. Whenever an element
external to the federation space is used, one needs to use a \emph{model slot}.
A model slot is a mediation entity in charge of giving access to external
elements using a \emph{technology adapter}\footnote{It is a reusable library
that defines connections between the \FML execution engine and a particular
technological space.}.

>>>>

A parallel to object-oriented approach can be useful to understand
\FML\footnote{Some features of \FML do not exist in object oriented
approach.}\!.  A concept corresponds to a class, its properties to the
attributes of the class and its behaviors to the methods of the class. These
properties have types defining the kind of value the role will point at
runtime. Whenever an element external to the federation space is used, one
needs to use a \emph{model slot}.  A model slot is a mediation entity in charge
of giving access to external elements using a \emph{technology
adapter}\footnote{It is a reusable library that defines connections between the
\FML execution engine and a particular technological space.}.
